\textbf{\sc Towards Deliberative Control of Autonomous Robots}

### 2012-02-15 trunk/arch.tex
updates

The synchronization process also supports the tracking of plan
execution. It does so by specifying token parameters such as time
points that are propagated through the plan in order to identify if
the plan remains valid -- as in our example -- or that it cannot be
executed as it is. The later is often identified by the
synchronization failing to find a consistent solution. for example
dshould the \texttt{Going} observation we receive be to the
\texttt{hardwareStore}, this would break the current plan of our
reactor as we cannot go simultaneously at 2 different places as
illustrated in Fig. \ref{fig:shop:relax}-1. as synchronization is not
possible in this context our strategy is to fully relax all decisions
made by the previous plan steps by just keeping n the plan all the
past observations in both {\em external} and {\em internal} state
variables and the exsiting {\em internal} goals received by this
reactor (\texttt{Own(Milk)} in our example) resulting on the plrtial
plan sghowned in Fig. \ref{fig:shop:relax}-2. In this process the
reactor inform the agent that all {\em external} goals it requested
for the future are note valid anymore which often result in the ownere
of htese timelines to not have to maintain this goal anynmore.

\begin{figure}[!htbp]
  \centering
  \includegraphics[width=0.7\columnwidth]{figs/shoping_exec_relax}  
  \caption{Illustration of a conflict during synchronization and the
    resulting relaxed plan for recovery} 
  \label{fig:shop:relax}
\end{figure}

As the plan is not anymore in the way the synchronization can resume
and find a solution as we initial lly described. The newly pending
goals will enforce at the next \texttt{step} to resumed deliberation
on this new fully relaxed partial plan. By the simple use of
synchronization the reactor was not only able to identify that its
plan was not executable anymore but recover from it while offering a
new incomplete partial plan to be resolved during the next
deliberation \texttt{steps}. This on its own ogfer the core
functionality one should except to close the loop between planning and
execution in the sense that synchronization plays the role of what is
typically named as the {\em Executive} in other architectures
{\em\color{red} references to diverse archis, 3-tiered, laas, claraty,
  B Wiliams, and many more}.

In our case though the interaction between planning and execution does
not stop at this level. A core point of the overal schedulling of both
{\em synchronization} and {\em planning} steps resides on our
architecture enforsincing that the synchroniuzation process can occur
in between any step of the plan. This lead us to the fact that not
only synchronization is imnfluenced by the outcome of planning but
this influence goes also in the alternate direction. Specifically when
synchronuiation occuers before we found a complete plan, it will
inject as we described new facts (the {\em external} observations and
resulting {\em internal} state) in the plan database. This
informatiuon will be present when the next planning \texttt{step} will
resume. Therefore they are not intergal part of the plan resolution
(generating potentially new flaws for the planner or contributing to
resolve previously exisiting flaws). The planning process is therefore
perturbed internallyand fully informed on how the world evolves as it
is planning.  This aspect trueluy contrast to other approaches we have
identified in the literature which avoid to perturb the planner during
it search as it is not compatible with the ``off-line planning''
assumption.

By our design choices -- both at the architecture level and the
integration of the \eu framework for embedded deliberation -- we
were able to implement an architecture that avoid this limitation
while remaining in a formal frame that still allow for deliberation
and model-based agent control. We believe that this tighter
integration of planning and execution allow the system to ba more
acute of its environment allowing better informaed decision and
tighter reaction. This is possible while still integrating information
such as a long latency for the reactors as long as one can ensure that
synchronization of al the reactors and deliberation steps can be done
in a time that is resonably small in comparison of the agent tick
duration.

>>>>

Synchronization also supports the tracking of plan execution. It does
so by specifying token parameters such as time points that are
propagated through the plan in order to identify if the plan remains
valid -- as in our example -- or that it cannot be executed as it
is. The later is often identified by the synchronization failing to
find a consistent solution. For example should the \texttt{Going}
observation received be to the \texttt{hardwareStore}, this would
break the current partial plan in the reactor as the robot cannot
possible be going simultaneously to $2$ different locations; see
Fig. \ref{fig:shop:relax1}. As synchronization is not possible in such
a situation the strategy followed is to relax all decisions made by
previous plan steps. This is done by keeping all past observations in
both {\em external} and {\em internal} state variables as well as the
existing {\em internal} goals (\texttt{Own(Milk)} in this example)
received by this reactor. The resulting partial plan is shown in
Fig. \ref{fig:shop:relax2}. In this process the reactor informs the
agent that all {\em external} goals it requested for the future are no
longer valid which results in turn, in timeline owners not having to
maintain such goals.

\begin{figure}[!htbp]
  \centering
  \subfloat[Conflicting Observation]{\label{fig:shop:relax1}\includegraphics[width=0.7\columnwidth]{figs/shoping_exec_relax-1}}\\
  \subfloat[Relaxed Partial Plan]{\label{fig:shop:relax2}\includegraphics[width=0.7\columnwidth]{figs/shoping_exec_relax-2}}
  \caption{\small Illustration of a conflict during synchronization
    and the resulting relaxed plan for recovery.}
\end{figure}

As the plan is no longer conflicted, synchronization can resume and
find a solution described above. Newly pending goals would be enforced
at the next \texttt{step} to resume deliberation on this relaxed
partial plan. By using synchronization the reactor was not only able
to identify that its plan was not consistent but able to recover from
it by offering a new incomplete partial plan to be resolved in the
next deliberation \texttt{steps}. % This on its own offer the core
% functionality one should except to close the loop between planning and
% execution in the sense that 
Synchronization plays the role of what is typically termed as the {\em
  Executive} in other architectures \cite{gat98, alami:1998p820,
  mus98, williams03, Nesnas:2003do}.

In \rx however the interaction between planning and execution does not
stop at this level. The overall scheduling of both {\em
  synchronization} and {\em planning} is such that the synchronization
can occur in between any planning step. Not only is synchronization
influenced by the outcome, but it also influences
planning. Specifically when synchronization occurs before a complete
plan is found, it will inject new facts ({\em external} observations
and resulting {\em internal} state) in the plan database available for
inference when the next planning \texttt{step} resumes. Therefore they
\comment{what is the ``they''?} are not integral part of the plan
resolution (generating potentially new flaws for the planner or
contributing to resolve previously existing flaws). The planning
process is therefore perturbed internally and fully informed by how
the world is evolving even as it is planning.  This specific aspect
contrasts with other approaches we have which avoid perturbing the
planner during its search as it is not compatible with the ``off-line
planning'' assumption.

By our design choices -- both at the architecture level and the
integration of the \eu framework for embedded deliberation -- we are
able to implement an architecture that avoids this critical off-line
planning limitation while remaining within a formal framework that
allows for deliberation and model-based agent control. We believe that
this tight integration of planning and execution allows the system to
be more acute vis-a-vis the environment allowing informed
decision-making and a tighter reaction loop. This is possible while
integrating information despite a long latency for the reactors, as
long as one can ensure that synchronization of all reactors and
deliberation steps can be done within a time that is resonably small
in comparison to the agent tick duration.
